---
title: "Reproducible Research: Peer Assessment 1"
output: 
html_document:
keep_md: true
---


## Loading and preprocessing the data


```{r LoadData,echo=TRUE}
temp <- tempfile()

download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp)
unzip(temp)
ACT <- read.csv("activity.csv")

unlink(temp) 
```

## What is mean total number of steps taken per day?
```{r Meanstepsday,echo=TRUE}
ACTmd<-tapply(ACT$step, ACT$date, sum)
hist(ACTmd,breaks=20, main="Total number of steps per day")
meansds<-summary(ACTmd)
meansds
meansd<-meansds["Mean"]
meansd
meansds["Median"]
```


## What is the average daily activity pattern?

```{r AVGdaily, echo=TRUE}
timei<-tapply(ACT$step,ACT$interval,mean,na.rm=TRUE)
plot(timei,x=names(timei),type="l",ylab="Avgstepsperinterval", xlab="Interval")
s<-sort(timei)
max<-s[length(s)]
max
```
## Imputing missing values
```{r Totalna, echo=TRUE}
na<-is.na(ACT)
sum(na)
```
###Here is the strategy to filling NAs,filling NAs with the mean for the 5-minute interval and create a dataset new

```{r FillingNAs, echo=TRUE}
meani <- aggregate(ACT$step ~ interval, data=ACT, mean)
names(meani)[2] <- "meanstep"
com <- merge(ACT, meani)
com$step[is.na(com$step)] <- com$meanstep[is.na(com$step)]
com$meanstep <- NULL

```

```{r newdataset, echo=TRUE}

com1<-com[,c(4,3,1)]

newdata<-com1[order(com1$date,com1$interval),]  
head(newdata)
```
###Histogram of total steps each day and mean and median of total steps.

```{r total steps rach day, echo=TRUE}
tstep<-tapply(newdata$step, newdata$date, sum)
hist(tstep, breaks=20)
s<-summary(tstep)
s["Mean"]
s["Median"]
```
Conclusion:The mean didn't change after filling the NAs with mean value of non-NA dataset; The median increased a little bit.

## Are there differences in activity patterns between weekdays and weekends?
```{r ActivityPatterncCompare, echo=TRUE}
newdata$wd<-weekdays(as.Date(newdata$date))
newdata$wdate=ifelse((newdata$wd=="Sunday"|newdata$wd=="Saturday"), "weekend", "weekday")
tail(newdata,20)

means<-aggregate(step~interval+wdate,data=newdata,FUN=mean)
       head(means)
        tail(means)        
```
###Panel plot compare the average steps per 5 minute between weekdays and weekends

```{r PanelPlotCompareAvgStep, echo=TRUE }
        library(grid)
        library (lattice)
p<-xyplot(step~interval|wdate, type="l", data=means, ylab="number of steps",layout=c(1,2) )
        print(p)
```

According to the plot, the activity patterns between weekdays and weekend are slightly different in the miidle intervals.